The LSST-DESC 3x2pt Tomography Optimization Challenge

### 2021-08-06 paper/paper.tex
correction

Authors AP, CRB, ESC, BMOF, EJG, and GT are collaborators from outside the
Dark Energy Science Collaboration included here under a DESC publication policy exemption.

>>>>

Authors CRB, ESC, BMOF, EJG, and GT are collaborators from outside the
Dark Energy Science Collaboration included here under a DESC publication policy exemption.
